Supplementary Materials

### 2023-02-08 analysis/paper/paper.qmd
fix: broken links after renaming to analysis

# upload data
metadata <- read_tsv(here("inst/data/raw_data/metadata.tsv"))
demography <- read_csv(here("inst/data/raw_data/demography.csv"))
lloq <- read_tsv(here("inst/data/raw_data/lloq.tsv"))
uhplc_data_comb <- read_csv(here("inst/data/derived_data/uhplc-data_combined.csv"))
dental_inv <- read_csv(here("inst/data/raw_data/dental-inv.csv"))
caries <- read_csv(here("inst/data/raw_data/caries.csv"))
periodont <- read_csv(here("inst/data/raw_data/periodontitis.csv"))
periap <- read_csv(here("inst/data/raw_data/periapical.csv"))
calculus <- read_csv(here("inst/data/raw_data/calculus.csv"))
calculus_full <- read_csv(here("inst/data/raw_data/calculus_full.csv"))
sinusitis_clean <- read_csv(here("inst/data/derived_data/sinusitis_cleaned.csv"))
path_cond_clean <- read_csv(here("inst/data/derived_data/path-conditions_cleaned.csv"))

source(here("inst/scripts/setup-qmd.R"))
#source(here("inst/supplementary-materials/supp-mat.qmd"), local = knitr::knit_global())
# set viridis as default pallette

>>>>

# upload data
metadata <- read_tsv(here("analysis/data/raw_data/metadata.tsv"))
demography <- read_csv(here("analysis/data/raw_data/demography.csv"))
lloq <- read_tsv(here("analysis/data/raw_data/lloq.tsv"))
uhplc_data_comb <- read_csv(here("analysis/data/derived_data/uhplc-data_combined.csv"))
dental_inv <- read_csv(here("analysis/data/raw_data/dental-inv.csv"))
caries <- read_csv(here("analysis/data/raw_data/caries.csv"))
periodont <- read_csv(here("analysis/data/raw_data/periodontitis.csv"))
periap <- read_csv(here("analysis/data/raw_data/periapical.csv"))
#calculus <- read_csv(here("analysis/data/raw_data/calculus.csv"))
calculus_full <- read_csv(here("analysis/data/raw_data/calculus_full.csv"))
sinusitis_clean <- read_csv(here("analysis/data/derived_data/sinusitis_cleaned.csv"))
path_cond_clean <- read_csv(here("analysis/data/derived_data/path-conditions_cleaned.csv"))

source(here("analysis/scripts/setup-qmd.R"))
#source(here("analysis/supplementary-materials/supp-mat.qmd"), local = knitr::knit_global())
# set viridis as default pallette

### 2023-02-08 analysis/supplementary-materials/supp-mat.qmd
fix: broken links after renaming to analysis

# upload data
metadata <- read_tsv(here("inst/data/raw_data/metadata.tsv"))
demography <- read_csv(here("inst/data/raw_data/demography.csv"))
lloq <- read_tsv(here("inst/data/raw_data/lloq.tsv"))
uhplc_data_comb <- read_csv(here("inst/data/derived_data/uhplc-data_combined.csv"))
#uhplc_calculus <- read_csv(here("inst/data/derived_data/uhplc-calculus_cleaned.csv"))
dental_inv <- read_csv(here("inst/data/raw_data/dental-inv.csv"))
caries <- read_csv(here("inst/data/raw_data/caries.csv"))
periodont <- read_csv(here("inst/data/raw_data/periodontitis.csv"))
periap <- read_csv(here("inst/data/raw_data/periapical.csv"))
calculus <- read_csv(here("inst/data/raw_data/calculus.csv"))
calculus_full <- read_csv(here("inst/data/raw_data/calculus_full.csv"))
sinusitis_clean <- read_csv(here("inst/data/derived_data/sinusitis_cleaned.csv"))
path_cond_clean <- read_csv(here("inst/data/derived_data/path-conditions_cleaned.csv"))

source(here("inst/scripts/setup-qmd.R"))
```

@@

### calculus

| variable | description |
|---|---|
| id | unique identifier for the individual |
| t11..t48 | Tooth number (FDI system) and deposit size (0-3) |

@@

@@

Caries were scored as the location on each individual tooth. Multiple locations on
a single tooth were separated with `;`. The size of caries was also
recorded, but not used in further analysis. Large caries that cover multiple
surfaces with an unknown origin were recorded as 'crown'. Caries counts were
extracted based on the number of locations recorded.

>>>>

# upload data
metadata <- read_tsv(here("analysis/data/raw_data/metadata.tsv"))
demography <- read_csv(here("analysis/data/raw_data/demography.csv"))
lloq <- read_tsv(here("analysis/data/raw_data/lloq.tsv"))
uhplc_data_comb <- read_csv(here("analysis/data/derived_data/uhplc-data_combined.csv"))
#uhplc_calculus <- read_csv(here("analysis/data/derived_data/uhplc-calculus_cleaned.csv"))
dental_inv <- read_csv(here("analysis/data/raw_data/dental-inv.csv"))
caries <- read_csv(here("analysis/data/raw_data/caries.csv"))
periodont <- read_csv(here("analysis/data/raw_data/periodontitis.csv"))
periap <- read_csv(here("analysis/data/raw_data/periapical.csv"))
calculus <- read_csv(here("analysis/data/raw_data/calculus.csv"))
calculus_full <- read_csv(here("analysis/data/raw_data/calculus_full.csv"))
sinusitis_clean <- read_csv(here("analysis/data/derived_data/sinusitis_cleaned.csv"))
path_cond_clean <- read_csv(here("analysis/data/derived_data/path-conditions_cleaned.csv"))

source(here("analysis/scripts/setup-qmd.R"))
```

@@

### calculus_full

| variable | description |
|---|---|
| id | unique identifier for the individual |
| t11_bucc..t48_ip | Tooth number (FDI system) and surface (bucc = buccal; lin = lingual; ip = interproximal) and deposit size (0-3) |

@@

Brief statement about amtl at site.

```{r}
dental_long %>% 
  group_by(id) %>% 
  amtl_ratio(.status = status, .add = T)
```

@@

<!--add a caries correction?-->
Caries were scored as the location on each individual tooth. Multiple locations on
a single tooth were separated with `;`. The size of caries was also
recorded, but not used in further analysis. Large caries that cover multiple
surfaces with an unknown origin were recorded as 'crown'. Caries counts were
extracted based on the number of locations recorded.
